Design and Implementation of Mobile Proxy\\ Case Study: Mobile Data Collection

### 2016-09-27 Paper/23215131-Aris Prawisudatama-Paper Thesis-3rd Rev/Paper.tex
Propose new Android GUI

\begin{listing}
    \caption{Install and start required bundles}
    \begin{minted}[showspaces=false,breaklines=true]{java}
> install http://knopflerfish.soedomoto.tk/jars/pgfw7/proxy-server-9.0.7.v20131107-dex.jar
Installed: Proxy Server (#10)
> start 10
2016-09-05 21:57:02.294:INFO:oejs.Server:BundleStart #10: jetty-9.0.z-SNAPSHOT
2016-09-05 21:57:02.455:INFO:oejs.ServerConnector:BundleStart #10: Started ServerConnector@698b6705{HTTP/1.1}{0.0.0.0:5555}
Started: Proxy Server (#10)
> install http://knopflerfish.soedomoto.tk/jars/pgfw7/se2016-bundle-0.1-SNAPSHOT-dex.jar
Installed: SE2016 - Application (#11)
> start 11
...
2016-09-05 21:57:33.147:INFO:oejsh.ContextHandler:BundleStart #11: Started o.e.j.s.ServletContextHandler@390161c7{/se2016,null,AVAILABLE}
Started: SE2016 - Application (#11)
> install http://knopflerfish.soedomoto.tk/jars/pgfw7/se2016-sync-bundle-0.1-SNAPSHOT-dex.jar
Installed: SE2016 - Sync Module (#12)
> start 12
Started: SE2016 - Sync Module (#12)
...
	\end{minted}
    \label{lst:start-bundle-remote}
\end{listing}

@@

>>>>

\begin{listing}
    \caption{Install and start required bundles}
    \begin{minted}[showspaces=false,breaklines=true]{java}
> install http://knopflerfish.soedomoto.tk/ jars/pgfw7/proxy-server-9.0.7.v20131107- dex.jar
Installed: Proxy Server (#10)
> start 10
2016-09-05 21:57:02.294:INFO:oejs.Server: BundleStart #10: jetty-9.0.z-SNAPSHOT
2016-09-05 21:57:02.455:INFO:oejs. ServerConnector: BundleStart #10: Started ServerConnector@698b6705 {HTTP/1.1}{0.0.0.0:5555}
Started: Proxy Server (#10)
> install http://knopflerfish.soedomoto.tk/ jars/pgfw7/se2016-bundle-0.1-SNAPSHOT- dex.jar
Installed: SE2016 - Application (#11)
> start 11
...
2016-09-05 21:57:33.147:INFO:oejsh. ContextHandler:BundleStart #11: Started o.e.j.s.ServletContextHandler@390161c7 {/se2016,null,AVAILABLE}
Started: SE2016 - Application (#11)
> install http://knopflerfish.soedomoto.tk/ jars/pgfw7/se2016-sync-bundle-0.1- SNAPSHOT-dex.jar
Installed: SE2016 - Sync Module (#12)
> start 12
Started: SE2016 - Sync Module (#12)
...
	\end{minted}
    \label{lst:start-bundle-remote}
\end{listing}

@@

\section{Testing}
\subsection{Response Time}
\begin{table}
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Response Time Test (ms)}
\label{tbl:response_time}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{|c||c|c|c|c|c|c|}
\hline
Transactions & \multicolumn{3}{|c|}{Without Proxy} & \multicolumn{3}{|c|}{With Proxy}\\
\hline
& Total & $\mu$ & $\sigma$ & Total & $\mu$ & $\sigma$\\
\hline
5 & 5043 &  &  & 121 &  & \\
\hline
110 & 50439 &  &  & 7442 &  & \\
\hline
1100 & 668605 &  &  & 405408 &  & \\
\hline
5500 & 2658179 &  &  & 2415957 &  & \\
\hline
\end{tabular}
\end{table}
